Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-11 paper/structureScene.tex
latexify

Application of the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets and state-of-the-art classifier demonstrates its potential. More precisely, features derived from the scattering transform consistently outperform Mel-frequency cepstral coefficients (MFCC) for both tasks.

@@

In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. Also, we resort to the use of SVMs with default parameters (C=1) for computing classification accuracy for the ASC task, as SVMs are widely used in the community and allows us to better root our work and focus our performance analysis on the earlier processing stages. Moreover, since the MFCCs are well established features and perform well in this task, they will be thoroughly used as baselines features in the experiments described in this paper.

@@

\ml{detail: put in experimental part using an enhanced version of the popular K-means algorithm known as K-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points. }

>>>>

Application of the proposed approach to the acoustic scene similarity retrieval and acoustic scene classification tasks on publicly available datasets and state-of-the-art classifier demonstrates its potential. More precisely, features derived from the scattering transform consistently outperform Mel-frequency cepstral coefficients (MFCCs) for both tasks.

@@

In this paper, we are interested in evaluating different algorithmic designs leading to different scene models, we therefore resort to straightforward ranking performance measures for the ASSR task. Also, we resort to the use of SVMs with default parameters ($C=1$) for computing classification accuracy for the ASC task, as SVMs are widely used in the community and allows us to better root our work and focus our performance analysis on the earlier processing stages. Moreover, since the MFCCs are well established features and perform well in this task, they will be thoroughly used as baselines features in the experiments described in this paper.

@@

\ml{detail: put in experimental part using an enhanced version of the popular K-means algorithm known as $K$-means$++$ \cite{arthur2007k}, which differs from k-means method in terms of selection of starting points. }
